From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam

### 2025-03-25 manuscript.qmd
Built site for gh-pages

---
title: 'From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam'
authors:
  - name: Haziq Jamil
    orcid: 0000-0003-3298-1010
    email: haziq.jamil@ubd.edu.bn
    url: 'https://haziqj.ml'
    corresponding: true
    affiliations:
      - name: Universiti Brunei Darussalam
        id: ubd
        department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410
  - name:
      given: Amira Barizah
      family: Noorosmawie
    orcid: 0009-0008-9334-7615
    affiliations:
      - ref: ubd        
  - name: 
      given: Hafeezul Waezz
      family: Rabu
    orcid: 0009-0008-0937-0071
    affiliations:
      - ref: ubd
  - name:
      given: Lutfi
      family: Abdul Razak
    orcid: 0000-0003-1681-0895
    email: lutfi.razak@ubd.edu.bn
    affiliations:
      - name: UBD School of Business and Economics
        id: ubdsbe
        # department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410         
date: 2025-03-23
date-modified: last-modified
abstract: |
  This article introduces the first publicly available data set for analysing the Brunei housing market, covering more than 30,000 property listings from 1993 to early 2025. The data set, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information. Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since its inception in 2015. Data collection involved manual transcription from archival sources and automated web scraping using programmatic techniques, supported by innovative processing with Large Language Models (LLMs) to codify unstructured text. The data set enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research. Although listing prices are only a proxy for market values and may deviate from actual sale prices due to negotiation dynamics and other factors, this data set still provides a valuable resource for quantitative analyses of housing market trends and for informing policy decisions.
keywords:
  - Housing Market
  - Brunei
  - Property Listings
  - Spatial Data
  - Web Scraping
  - Large Language Models
editor_options: 
  chunk_output_type: console
---

@@

>>>>

---
title: 'From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam'
authors:
  - name: Haziq Jamil
    orcid: 0000-0003-3298-1010
    email: haziq.jamil@ubd.edu.bn
    url: 'https://haziqj.ml'
    corresponding: true
    affiliations:
      - name: Universiti Brunei Darussalam
        id: ubd
        department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410
  - name:
      given: Amira Barizah
      family: Noorosmawie
    orcid: 0009-0008-9334-7615
    affiliations:
      - ref: ubd        
  - name: 
      given: Hafeezul Waezz
      family: Rabu
    orcid: 0009-0008-0937-0071
    affiliations:
      - ref: ubd
  - name:
      given: Lutfi
      family: Abdul Razak
    orcid: 0000-0003-1681-0895
    email: lutfi.razak@ubd.edu.bn
    affiliations:
      - name: UBD School of Business and Economics
        id: ubdsbe
        # department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410         
date: 2025-03-23
date-modified: last-modified
abstract: |
  This article introduces the first publicly available data set for analysing the Brunei housing market, covering more than 30,000 property listings from 1993 to early 2025. The data set, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information. Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since its inception in 2015. Data collection involved manual transcription from archival sources and automated web scraping using programmatic techniques, supported by innovative processing with Large Language Models (LLMs) to codify unstructured text. The data set enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research. Although listing prices are only a proxy for market values and may deviate from actual sale prices due to negotiation dynamics and other factors, this data set still provides a valuable resource for quantitative analyses of housing market trends and for informing policy decisions.
keywords:
  - Housing Market
  - Brunei
  - Property Listings
  - Spatial Data
  - Web Scraping
  - Large Language Models
manuscript-url: https://bruneiverse.github.io/house-data
editor_options: 
  chunk_output_type: console
---

@@

::: {.content-visible when-format="pdf"}

# Citation

For attribution, please cite this work as:

> H. Jamil, A.B. Noorosmawie, H.W. Rabu, L. Abdul Razak, From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam, Data in Brief (2025). <https://doi.org/10.1016/j.dib.2025.111505>.

:::
